### 2010-01-29 doc/manuals/configuration/configuration_manual.tex
Rewriting service configuration documentation. Not complete yet. Please come with feedback.

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Martin Savko},
  pdftitle = {ARC configuration manual},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large ARC configuration manual}\Large \par}
\vspace*{0.5cm}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large Zsombor Nagy\footnote{zsombor@niif.hu} \large \par}
    {\centering \large Ferenc Szalai\footnote{szferi@wsbricks.com} \large \par}
    {\centering \large Martin Savko\footnote{martin.savko@gmail.com} \large \par}
\end{titlepage}

@@

The arched daemon's configuration file contains general information about the daemon's environment (pid file, log file, log level, library paths, plugins), and it contains one (or more) message chains, which specifies how the different services are connected to the outside world. The daemon's listening interface, certificates used, and the HTTP path of the services are among the things specified in the chain. This part contains also the configuration specifics for each service.

A chain could contain multiple types of components: message chain components (called MCCs) which provide TCP, TLS, HTTP and SOAP support; the plexer, which connects different HTTP paths to different services; and the services themselves with all their specific configuration details.

The configuration file is in XML format, with XML schemas and namespaces given and documented.

For typical deployment scenarios there is an additional mechanism to create an XML configuration on-the-fly based on XML templates (called “profiles”) and more administrator-friendly INI configuration files.

Configuration related arched command line switches:

\begin{verbatim}
	-c <xml config file>
	-i <ini config file>
	-d
	-s <xml schema>
\end{verbatim}

By default the daemon looks for the configuration files in the following order: first /etc/arc/server.ini, then if it is not found: /etc/arc/server.xml. However user can define which configuration  should be used with the -c or -i command line argument. If accidentally both of them is defined then the -i has greater priority.

In order the check the generated XML configuration the -d options can be used. If used, arched will  print the XML configuration to the standard output and then stop.

\section{XML level configuration}

\begin{itemize}
		\item The first part of the config is the “Server” part, which contains the path of the pid file, and the path of the log file, and the verbosity of the logging.
		\item The second part of the config is the “ModuleManager” part, which contains the path to the directory with the ARC libraries.
		\item The third part is the “Plugins” part with the list of 'plugins' (e.g. message chain components, services) used in this config.
		\item The fourth part is the “Chain” part, which contains the description of the message chain, which connects the services to the network. (It is possible to have more than one chain in one configuration.) A chain could contain the message chain components, the plexer and the services.
		\begin{itemize}
			\item The TCP message chain component does the listening on the network interface. This is the place to set the IP version to use, the IP and port to listen to.
			\item The TLS message chain component implements the security layer. This is the place to set the server-side key and the certificate, and the directory of the trusted CA certificates.
			\item The configuration of the HTTP and the SOAP message components most probably don't need to be changed.
			\item The Plexer component has a list of all available services, and has a HTTP path for each of them. The path is a regular expression, the incoming HTTP requests will be sent to the service which has a matching path in the Plexer config.
			\item Then come the specific configurations of all the services which will be running in this arched.
		\end{itemize}
\end{itemize}

\subsection{The service only gets its own config}

It is important to know that the services will not be able to get the whole configuration, they will only get their part, so everything a service should know have to be specified in its configuration part, e.g. a service would not know the IP or the port of the server, the HTTP path to itself or the path of the key and certificate file unless these are specified in the service configuration part too.

Because some services would establish some network connection while running (e.g. to send SOAP messages to other services), and these connections would most probably be secure HTTPS connection, these services may have a part where a client-side key and certificate file have to be specified which can be used to establish connection.

A service most probably would want to advertise its URL by registering itself to an information indexing service (called ISIS), in order to do this, the full URL of the service should be put into the configuration part of the service. This means that if the daemon's interface (port or hostname) would be changed, all these URLs should be modified too.

\subsection{Summary of where to change things}
\begin{itemize}
	\item pidfile, logfile, loglevel: the “Server” part
	\item path to the ARC libraries/modules/plugins: the “ModuleManager” part
	\item listening interface (port, IP, IP version): the TCP Component in the “Chain” part; and maybe the URLs of the services should be changed also in the configuration of the services.
	\item path to the server-side key and certificate files and CA dir: the TLS Component in the “Chain” part
	\item path to the client-side key and certificate files and CA dir: in the configuration of the individual services in the “Chain” part
	\item the HTTP path of the services: the Plexer in the “Chain” part, the paths are specified in regular expressions; and maybe the URL of the service should be changed also in the configuration of the service itself.
	\item the URL of the information indexing service (ISIS) where a service should advertise itself: in the config of each services in the “Chain” part
\end{itemize}

There are documentations and XML schemas for the possible configuration options of the message chain components (MCCs) and for all the services (TODO: link to some docs and stuff)

\section{INI style configuration}

Because the parameters which a system administrator would want to change while configuring arched are spread across the whole XML configuration file and sometimes even repeated several times, and because there are lots of things in the XML configuration file which would be always the same for a given deployment-scenario, it is possible to create different configuration profiles for different scenarios, and then configure these profiles with configuration files which are in a more user-friendly INI format containing key-value pairs grouped in sections. Then the XML config is generated from the given profile and the INI config. (A profile is basically a full XML configuration, but has some extra details about which part of the XML should be overwritten with which INI configuration parameter.)

For example there is a profile for a secure Echo service which contains a working set of message chain components and the Echo service with reasonable defaults for the paths of libraries, logfile, pidfile, certificates, the port to listen, the HTTP path of the service, etc. Then the system administrator can create an INI config which only contains the things which need to be non-default, e.g. if the key and certificate files are in a non-standard directory, the correct paths could be specified in the INI config, and these paths then would be put into the profile everywhere where needed (even multiple times).

Or if there is a profile with several services, all of them registering to an information index service (ISIS), which means that each service has the URL of the ISIS service in its config, this URL could be changed by adding one line to the INI config with the new URL, which makes this URL inserted into the config of each services.

\subsection{Issues}

Using the INI config is much easier for the system administrator than figuring out where to modify the XML config in order to change some paths or URLs. However using the INI config is much less flexible then using the XML config. Everything depends on the profiles. If the system administrator would need a specific set of services, and there is no profile for that, then the INI config can't be used. Or if there is profile but a given configuration parameter is not given in the profile, then it cannot be set in the INI config.

Another issue is that for each individual profile a separate documentation would be needed, because a profile can use arbitrary INI tags. e.g. the INI tag for setting the log level could be “loglevel” in one profile and it could be “debug” in another, or something completely different in the third one. The way to set the path to the directory of the trusted CAs' certificates could be “cacert=path” or “cacertificatesdir=path” depending which profile is in use. Currently there are example INI configs for most of the existing profiles, which should give hints about the possible INI tags.

\subsection{INI section}

The key-value pairs in an INI file are grouped into sections, like this:

\begin{verbatim}
	key1=value1
	key2=value2

	[section1]
	key1=value11
	key3=value3

	[section2]
	key5=value5
\end{verbatim}

The key-value pairs before the first section name are in the “common” section. The sections are used to selectively override arguments. e.g. the profile could say that it needs the value for “key1”, and then it could specify that it needs the value from the “common” section only, or from the |”section1” section only, or it could say that it needs the value from either of these two sections and the value from “section1” overrides the value from the “common” section, or vice versa.

For a more specific example, if there is a client-side key file given in the common section, then the profile could specify for each service, that it should use this key file unless there is a different key file specified in the section of the given service. This means that if there is an INI section for the service, and it contains a path to the key file, then that path will be used, but if it does not contain a path, then the common key path will be used from the “common” section.

\subsection{Profiles}

The profile is a full XML service configuration with some additional XML attributes about which part of the XML should be overwritten by which INI parameter. Let's look at this part of a profile:

\begin{verbatim}
	<infosys:URL inisections='register ahash' initag=\verb!index_server1!/>
\end{verbatim}

The initag attribute tells the key of the parameter, the inisections attribute specifies a list of sections with the last one having the highest priority. This XML tag here is empty, which means that it's default value is an empty string.

\begin{itemize}
	\item If the INI contains a key \verb!index_server1! somewhere in the 'register' or 'ahash' sections, then the value from that key would be put into this XML node.
	\item If there is an \verb!index_server1! key in both the 'register' and the 'ahash' section, then the value from the 'ahash' section would be used, it has the higher priority.
	\item If there is no \verb!index_server1! key in none of these two sections in the INI config, then this 'infosys:URL' tag will still be in the generated XML config, but with an empty content.
\end{itemize}

This part has a non-empty default:

\begin{verbatim}
	<cfg:File inisections='common' initag='logfile'>/var/log/arched.log</cfg:File>
\end{verbatim}

This means if that would be a 'logfile' key in the 'common' section of the INI configuration file, then this default value will be overwritten by the value of that key from the INI file. If there is no key called 'logfile' in the 'common' section of the INI file, then the generated XML config will contain the given default value.

\subsection{Limitations}

Currently overwriting XML attributes are not supported. e.g. the id attribute of:

\begin{verbatim}
	<next id='tls'/>
\end{verbatim}

can not be overwritten by the INI config.

Currently there is no support for XML tags with variable number of occurrences. This means that if there would be a part in the XML config like this:

\begin{verbatim}
	<ISISURL>the URL of an ISIS service</ISISURL>
	<ISISURL>the URL of another ISIS service</ISISURL>
	<ISISURL>the URL of a third ISIS service</ISISURL>
\end{verbatim}

It is not possible to control the number of ISISURL tags from the INI config. If there are three such lines in the profile, then there will be three lines in the generated XML config, no matter how many URLs are specified in the INI config. A workaround could be using empty defaults, like this:

\begin{verbatim}
	<lib:ISISURL inisections='register librarian' initag=\verb!index_server1!/>
	<lib:ISISURL inisections='register librarian' initag='index_server2'/>
	<lib:ISISURL inisections='register librarian' initag='index_server3'/>
\end{verbatim}

Then the INI config could be like this:

\begin{verbatim}
	[register]
	index_server1=the URL of an ISIS service
	index_server2=the URL of another ISIS service
\end{verbatim}

Which means that the first and second ISISURL line would be filled with data from the INI, and the third one would be left empty. For this to work, it should be supported by the service itself, e.g. the service should throw out empty ISISURLs.

Here it was needed to use different initags for the three ISISURLs, because if same initags would be used like this:

\begin{verbatim}
	<lib:ISISURL inisections='register librarian' initag='index_server'/>
	<lib:ISISURL inisections='register librarian' initag='index_server'/>
	<lib:ISISURL inisections='register librarian' initag='index_server'/>
\end{verbatim}

Then this INI config would cause unexpected results:

\begin{verbatim}
	[register]
	index_server=the URL of an ISIS service
	index_server=the URL of another ISIS service
\end{verbatim}

This INI config would generate this XML config from that profile:

\begin{verbatim}
	<lib:ISISURL>the URL of another ISIS service</lib:ISISURL>
	<lib:ISISURL>the URL of another ISIS service</lib:ISISURL>
	<lib:ISISURL>the URL of another ISIS service</lib:ISISURL>
\end{verbatim}

Which is the same URL three times, because the last value of the \verb!index_server! tag would be inserted into each places.

There are future plans for adding support for this kind of simple multiplicity, but there are more complex cases which are not trivial to handle. e.g. in order to register to multiple ISIS services, the path to the key and certificate files should be given for each ISIS service even though they most probably would be the same. This part would register to one ISIS service:

\begin{verbatim}
	<infosys:Registrar>
		<infosys:URL inisections='register shepherd' initag='index_server'/>
		<infosys:KeyPath inisections='common shepherd' initag='client_key'/>
		<infosys:CertificatePath inisections='common shepherd' initag='client_cert'/>
		<infosys:CACertificatesDir inisections='common shepherd' initag='cacert'/>
	</infosys:Registrar>
\end{verbatim}

It is possible that we want to register only to one ISIS or two or maybe three or more, then for each of them this section should be repeated. Currently the workaround looks like this:

\begin{verbatim}
	<infosys:Registrar>
		<infosys:URL inisections='register shepherd' initag=\verb!index_server1!/>
		<infosys:KeyPath inisections='common shepherd' initag='client_key'/>
		<infosys:CertificatePath inisections='common shepherd' initag='client_cert'/>
		<infosys:CACertificatesDir inisections='common shepherd' initag='cacert'/>
	</infosys:Registrar>
	<infosys:Registrar>
		<infosys:URL inisections='register shepherd' initag='index_server2'/>
		<infosys:KeyPath inisections='common shepherd' initag='client_key'/>
		<infosys:CertificatePath inisections='common shepherd' initag='client_cert'/>
		<infosys:CACertificatesDir inisections='common shepherd' initag='cacert'/>
	</infosys:Registrar>
	<infosys:Registrar>
		<infosys:URL inisections='register shepherd' initag='index_server3'/>
		<infosys:KeyPath inisections='common shepherd' initag='client_key'/>
		<infosys:CertificatePath inisections='common shepherd' initag='client_cert'/>
		<infosys:CACertificatesDir inisections='common shepherd' initag='cacert'/>
	</infosys:Registrar>
\end{verbatim}

Which allows to register to up to three ISIS services, and has empty defaults in order to be able to configure only one or two or zero ISIS services. However, the ISIS registration part should handle the empty defaults, and throw them away.

\section{Examples}

The most up to date Profiles can be found in the Nordugrid SVN:

\verb!http://svn.nordugrid.org/trac/nordugrid/browser/arc1/branches/nox/src/hed/profiles!

Upon a successful installation (nordugrid-arc-nox-hed package when installing from binaries), all the example configuration files coming with the release can be found under

\verb!<instllation_directory>/share/arc/!

\end{document}

>>>>

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
\usepackage{array}
\usepackage{booktabs}
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Martin Skou Andersen},
  pdftitle = {WS-ARC service configuration manual},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
\definecolor{grey}{rgb}{0.9,0.9,0.9}

\usepackage{listings}
 \lstset{
         basicstyle=\small\ttfamily,
         numbers=none,
         numberstyle=\tiny,
         stepnumber=1,
         numbersep=5pt,
         tabsize=2,
         extendedchars=true,
         breaklines=true,
         keywordstyle=\color{red},
 %        keywordstyle=[1]\textbf,
 %        keywordstyle=[2]\textbf,
 %        keywordstyle=[3]\textbf,
 %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %
         stringstyle=\color{blue}\ttfamily,
         showspaces=false,
         showtabs=false,
         xleftmargin=17pt,
         frame=single,
         framexleftmargin=17pt,
         framexrightmargin=5pt,
         framexbottommargin=4pt,
         framextopmargin=4pt,
         backgroundcolor=\color{grey},
         showstringspaces=false
 }
 \lstloadlanguages{
  sh,
  XML
 }

% Make lineshift after paragrah...
\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
  {-3.25ex\@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\normalfont\normalsize\bfseries}}
\makeatother

 %
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

%%%%---- The title ----
{\centering \textsc{\Large WS-ARC service configuration manual}\Large \par}
\vspace*{0.5cm}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large Martin Skou Andersen\footnote{skou@nbi.dk} \large \par}
\end{titlepage}

@@

The Web Service (WS) Advanced Resource Connector (ARC) provides a great deal of
services which all share a common configuration interface. One or more services
can be specified in a configuration and the \texttt{arched} daemon should then
be used for starting the service(s). The configuration should be
specified in a file using either the relatively simple INI format, or the more
complex XML format.

INI configuration is the recommended way of configuring services for people who
are new to ARC or unfamiliar with WS-ARC configuration. However it is limited in
the sense that it relies on profiles. A profile is a configuration
template setup for one or more services, and common use case profiles exist for
most services and are installed per default. The limitation lies in the fact
that only services and options which are specified in the profile can be
configured in INI configuration, however the installed profiles should give
enough flexibility for common use cases. For a detailed description on INI
configuration see section~\ref{sec:INI configuration}. Profiles are further
discussed in section~\ref{sec:Profiles}.

XML configuration is the core format of WS-ARC configuration -- it
is used internally -- and thus it gives full flexibility when configuring
services. A detailed description of XML configuration can be found in
section~\ref{sec:XML configuration}.

The \texttt{arched} daemon, which is used to start WS-ARC services according to
the configuration is briefly discussed in section~\ref{sec:arched}.

\subsection{How to read this manual}
This manual is divided into the three independent sections INI configuration,
XML configuration and Profiles, and these can be read independent of each other.
Additionally the \texttt{arched} section describe the command with the same
name.

It should be noted that words typeset with the \texttt{typewriter} font should
be typed as written.

\section{INI configuration}\label{sec:INI configuration}
As mentioned in the introduction, INI configuration directly relies on profiles,
and a profile is a configuration template setup for one or more services. So
when creating a INI configuration file a choice of profile must be made. Only
one profile can be used in a given INI configuration. A standard WS-ARC
installation comes with a set of profiles and the list in
appendix~\ref{app:List of profiles} gives a short description of these. The
profiles will per default be installed into the \texttt{/usr/share/arc/profiles}
folder, where it is also possible to find an example INI configuration file for
each of the profiles.

A INI configuration file basically consist of sections, attribute-value pairs
and maybe comments and blank lines. In the following code-listing the syntax of
an INI configuration file is shown:
\begin{lstlisting}
# A comment
[ common ]
profile = <path-to-profile>

<attribute> = <value>
...
...

# Another comment
[ <section-name> ]
<attribute> = <value>
...
...
[ <another-section> ]
<attribute> = <value>
...
...
\end{lstlisting}

A section is specified by putting the name of the section inside brackets
(\texttt{[} and \texttt{]}), where the left bracket (\texttt{[}) must be the
first non white space character on the line. Any white space character after the
left bracket and before the right will not be part of the section name. Every
attribute-value pair belongs to the section which has be been defined
previously. If the file starts without declaring a section, then following
attributes will belong to the common section. Multiple sections with identical
names are different sections, except for the common section, which is special in
this respect and if multiple common sections exist these will be considered as
one.

The \texttt{profile} attribute is also a special, as it is used to indicate
which profile the INI configuration uses, and its value should be the
absolute path to the profile file. The \texttt{profile} attribute must be
located in the common section. If multiple \texttt{profile} attributes exist
only the first attribute will be used.

Attribute-value pairs are defined by specifying the name of the attribute
followed by an equal sign and then the value the attribute should take. It is
the first equal sign which separates the attribute from the value. If a line,
not defining a section, does not contain an equal then it will be ignored and if
it contains multiple equal signs then all but first equal sign will be part of
the value. Any white space before and after the attribute and value will be
ignored. Only attributes which have been defined in the selected profile will be
consideren by \texttt{arched}. For each profile in WS-ARC a corresponding INI
configuration file exist which defines sensible values and at the time list all
configurable attributes. When it comes to multiple attributes with identical
names defined in the same section, it is the selected profile which determines
if multiple attributes is allowed and will be interpreted or not. It is possible
that attributes from one section can override attributes from another section,
however this behaviour is completely determined by the profile.

Comments in the INI configuration file are specified by letting the first non
white space character be the sharp character (\texttt{\#}), and these will be
ignored by \texttt{arched}.

\subsection{Examples}
\subsubsection{Echo service}

\begin{lstlisting}
profile = /usr/share/arc/profiles/EchoService.xml

pidfile = /tmp/arched.pid
logfile = /tmp/arched.log
loglevel = INFO

port = 60000

cacert = /etc/grid-security/certificates
host_cert = /etc/grid-security/hostcert.pem
host_key = /etc/grid-security/hostkey.pem

[ echo ]
prefix = {{
suffix = }}
\end{lstlisting}

\subsubsection{Other service}

\subsection{Limitations}
Configuring WS-ARC services in INI format may pose some limitations, since this
configuration format depend on profiles. If one wants to configure a service
setup which is not covered by any of the available profiles, it is simply not
possible to configure that service setup in INI format and one has to use the
XML format described in section~\ref{sec:XML configuration}. It should however
be noted that it is easy to switch from INI to XML format since the
\texttt{arched} command provide a way to convert a INI configuration into XML.
See section~\ref{sec:arched} for further details.

\section{XML configuration}\label{sec:XML configuration}
\subsection{Overview}
XML configuration in WS-ARC provides full flexibility for configuring services,
and to construct an adequate configuration one need to address the following
subjects. If not done already, a choice on which service(s) being setup need to
be made and a short discussion of the available WS-ARC services is given in
section~\ref{sec:Service configuration}. Upon the choice of service(s) the
proper message chain need to be configured and a discussion about message chains
is given in section~\ref{sec:Message Chain}. Most people also want some kind of
security setup capable of allowing/denying certain users, which can be done with
security handlers and is discussed in section~\ref{sec:Security Handlers}.
Common configuration options like specifying plugins required for instance by
the message chain, and configuring logging, is discussed in
section~\ref{sec:General Daemon Configuration}. In
section~\ref{sec:XML examples} example XML configuration files are given.

\subsection{Service configuration}\label{sec:Service configuration}
The following services are part of WS-ARC and specific configuration details for
these are given in the respective references below:
\begin{description}
\item[A-REX]
  A-REX
\item[Chelonia]
\item[ISIS]
\item[Charon]
\item[hopi]
  hopi, a lightweight HTTP webserver, is described in details in \%\% REFERENCE.

\end{description}

\subsection{Message Chain}\label{sec:Message Chain}
To configure WS-ARC services, a basic knowledge about how these are
communicating with clients or other services is needed. WS-ARC uses a chain of
message components (MCCs) which serves different levels of functionality. In one
end it accepts messages from an interface and in the other a service processes
them and produce a response. Two types of MCCs exist, and they differ in that
the first type should be able to listen on some interface for messages, while
the other simply
receives messages from another MCC. The MCC then process the message and pass it
on to a single or multiple other MCCs or services. MCCs should be configured
using the XML element \texttt{Component}, where the \texttt{name} attribute
specifies the MCC to use. The following MCCs is part of WS-ARC:
\begin{description}
\item[\texttt{tcp.service}] Listens on the TCP interface, see
  section~\ref{sec:tcp-mcc},
\item[\texttt{tls.service}] Adds encryption layer to communication, see
  section~\ref{sec:tls-mcc},
\item[\texttt{http.service}] Processes HTTP messages, see
  section~\ref{sec:http-mcc},
%~ \item[\texttt{gsi.service}] Processes GSI messages, see
  %~ section~\ref{sec:gsi-mcc},
\item[\texttt{soap.service}] Processes SOAP messages, see
  section~\ref{sec:soap-mcc}.
\end{description}
Additionally a special MCC,
the Plexer, exist which is able to pass messages to different components simply
based on the endpoint the messages was sent to, and it should should be
configured using the \texttt{Plexer} element, see section~\ref{sec:plexer}. In
the end of the chain a service should be specified, using the  \texttt{Service}
element, where the \texttt{name} attribute indicates the given service.

A working configuration should then link a set of MCCs and services, starting
with a MCC that receives messages from some interface. The MCCs and services
should be uniquely identifiable, by setting the \texttt{id} attributes of these
elements. A MCC links to another or several MCCs or services using the
\texttt{next} element, where the \texttt{id} attribute specifies the \texttt{id}
of that MCC or service. The message chain should be contained in the root
element \texttt{ArcConfig}, which is shown in the conceptual configuration
example below:
\begin{lstlisting}[language=xml]
...
<Component name="mcc1.service" id="mcc1">
  <next id="mcc2"/>
</Component>
<Component name="mcc2.service" id="mcc2">
  <next id="service"/>
</Component>
<Service name="service" id="service"/>
...
\end{lstlisting}
For readability the message chain can be grouped into a \texttt{Chain} element
in one or more levels.

\subsubsection{TCP MCC}\label{sec:tcp-mcc}
The TCP message component is named \texttt{tcp.service} and should be the first
component in a chain. It is used to setup a server socket which will listen for
incoming connections. The socket can be configured using the \texttt{Listen}
element, which can occur multiple times and under each element the following
child elements can be specified:
\begin{description}
\item[\texttt{Interface}] This element specifies the interface which socket
  should listen on. If this element is not specified then the socket will listen
  on all available interfaces.
\item[\texttt{Port}] The port which the socket should bind to should be
  specified with this element. If no port is specified an error will be reported
  and this \texttt{Listen} element will be ignored.
\item[\texttt{Version}] The IP version can be specified by this element, and by
  default both version 4 and 6 will be used. It is possible to specify version 4
  or 6 only.
\item[\texttt{NoDelay}] By default Nagle's algorithm is used for sending data,
  however if the \texttt{NoDelay} element is set to \texttt{true} data will be
  send when ready.
\item[\texttt{Timeout}] Specifies how much time, in seconds, there should be
  used on waiting for a client response. If no client response is obtained
  before timeout the connection is dropped. The default value is 60 seconds.
\end{description}
It is also possible to put a limit on incoming connections, and how these should
be handled if the limit is reached. The limit can only be put on all configured
interfaces, and not per interface. The \texttt{Limit} element specifies the
limit on incoming connections, and the \texttt{drop} attribute specifies whether
new connections, above the limit, will be put on hold (default) or if they
should be dropped, which is specified by setting the attribute to \texttt{true}.

An example of a TCP MCC configuration using the described elements is shown
below:
\begin{lstlisting}[language=xml]
...
<Component name="tcp.service" id="tcp">
  <Listen>
    <Interface>w.x.y.z</Interface>
    <Port>44444</Port>
    <Version>4</Version>
    <NoDelay>true</NoDelay>
    <Timeout>120</Timeout>
  </Listen>
  <Listen>
    <Interface>a:b:c:d:e:f:g:h</Interface>
    <Port>55555</Port>
    <Version>6</Version>
    <NoDelay>false</NoDelay>
    <Timeout>20</Timeout>
  </Listen>
  <Limit drop="true">30</Limit>
</Component>
...
\end{lstlisting}

\subsubsection{TLS MCC}\label{sec:tls-mcc}
A security layer can be configured with the TLS MCC, named \texttt{tls.service},
and it should be put on top of a TCP MCC. By default it is able to understand
the SSLv2, SSLv3 and TLSv1 protocols, however the \texttt{Handshake} element can
be used to specify another behaviour. The supported values for the
\texttt{Handshake} element are \texttt{TLS} (default) and \texttt{SSLv3}, where
specifying the latter will configure a MCC which only understand the SSLv3
protocol. If other values than the mentioned ones are given, then \texttt{TLS}
will be used.

For the TLS MCC to function, it should have access to a host key-certificate
pair. The key should be the private one, and it should not be password
protected. The path to the key-certificate pair can be specified by using the
\texttt{KeyPath} and \texttt{CertificatePath} elements. If the \texttt{KeyPath}
element is not specified the default path
\texttt{/etc/grid-security/hostkey.pem} will be used, and likewise if the
\texttt{CertificatePath} element is not specified the default path
\texttt{/etc/grid-security/hostcert.pem} will be used. The supported key and
certificate formats are PEM and DER.

When establishing a connection with a client, the client certificate are per
default verified against the Certificate Authority (CA) certificates, known to
the TLS MCC. The CA certificates used for verification can be specified with
either the \texttt{CACertificatesDir} or the \texttt{CACertificatePath} element,
or both elements can be used. The \texttt{CACertificatesDir} element should
point to a directory containing one or more CA certificates (in PEM format). The
files should each contain exactly one certificate, and should be named by the
hash value of the CA subject name. CA certificates provided by NorduGrid uses
this option. The \texttt{CACertificatePath} element should point to a file
containing one or more CA certificates (in PEM format) identified by:
\begin{lstlisting}
  -----BEGIN CERTIFICATE-----
  ... (CA certificate in base64 encoding) ...
  -----END CERTIFICATE-----
\end{lstlisting}
sequences. If both elements have been specified, CA certificates will first be
looked up in the file pointed to by the \texttt{CACertificatePath} element and
then in the directory pointed to by the \texttt{CACertificatesDir} element. If
none of the two elements have been specified, then the
\texttt{CACertificatesDir} element will be initialised to the
\texttt{/etc/grid-security/certificates} location. Client certificate
verification can also be skipped, which is done by setting the
\texttt{ClientAuthn} element to \texttt{false}.

\begin{lstlisting}[language=xml]
...
<Component name="tls.service" id="tls">
  <KeyPath></KeyPath>
  <CertificatePath></CertificatePath>
  <CACertificatePath></CACertificatePath>
  <CACertificatesDir></CACertificatesDir>
  <ClientAuthn></ClientAuthn>
  <Handshake>SSLv3</Handshake>
</Component>
...
\end{lstlisting}

%~ \paragraph{Globus Policy}
%~ attribute \texttt{PolicyGlobus} (CACertificatePath).
%~
%~ \paragraph{Trusted VOMS Credentials}
%~ \texttt{VOMSCertTrustDNChain}
%~ <xsd:sequence>
  %~ \texttt{VOMSCertTrustDN}
  %~ \texttt{VOMSCertTrustRegex}
%~ </xsd:sequence>
%~ The DN list of the trusted voms server credential;
%~ in the AC part of voms proxy certificate, voms proxy
%~ certificate comes with the server certificate which is
%~ used to sign the AC. So when verifying the AC on the
%~ AC-consuming side (in ARC1, it is the MCCTLS which will
%~ consumes the AC), the server certificate will be checked
%~ against a trusted DN list. Only if the DN and issuer's
%~ DN of server certificate exactly matches the DN list
%~ in the configuration under TLS component, the AC can be trusted
%~
%~ \texttt{VOMSCertTrustDNChainsLocation}
%~ DN list in an external file, which is in the same format as VOMSCertTrustDNChain
%~
%~ \begin{lstlisting}[language=xml]
%~ ...
%~ <Component name="tls.service" id="tls">
  %~ <VOMSCertTrustDNChain>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustDN></VOMSCertTrustDN>
    %~ <VOMSCertTrustRegex></VOMSCertTrustRegex>
  %~ </VOMSCertTrustDNChain>
%~ </Component>
%~ ...
%~ \end{lstlisting}

\subsubsection{HTTP MCC}\label{sec:http-mcc}
The HTTP protocol is supported by the HTTP MCC named \texttt{http.service}, and
it should either be put on top of the TCP or TLS MCC. A working configuration of
this MCC is simple, since it should only use the \texttt{next} element which
must have a value equal to one of the HTTP request methods. An example of a HTTP
MCC configuration is shown below.

\begin{lstlisting}[language=xml]
...
<Component name="http.service">
  <next id="component1">GET</next>
  <next id="component2">POST</next>
  <next id="component3">PUT</next>
</Component>
...
\end{lstlisting}

%~ \subsubsection{GSI MCC}\label{sec:gsi-mcc}
%~ \texttt{KeyPath} Location of private key.
%~
%~ \texttt{CertificatePath} Location of public certificate.
%~
%~ \texttt{ProxyPath} Location of proxy credentials - includes certificates, key
%~ and chain of involved certificates. Overwrites elements \texttt{KeyPath} and
%~ \texttt{CertificatePath}.

\subsubsection{SOAP MCC}\label{sec:soap-mcc}
SOAP is supported by the SOAP MCC, named \texttt{soap.service}. It parses and
processes incoming messages as SOAP messages. This component should be put right
after the HTTP MCC in the message chain. The component is needed by most of the
services in WS-ARC. The only option which should be configured for the SOAP MCC
is to which component or service the valid SOAP messages should be directed to,
and it is done with the \texttt{next} element as for the other components.

\subsubsection{Plexer}\label{sec:plexer}
The Plexer is a special MCC which filters messages based on their URL endpoints.
One or more regular expressions (POSIX extended) should be defined using one or
more \texttt{next} elements, and these will then be used to filter incoming
messages, thus forwarding messages, where the path of the endpoint URL matched a
given regular expression, to the component or service specified by the
\texttt{id} attribute of the corresponding \texttt{next} element. At the first
match the message will be forwarded to the respective component or service and
no more expressions will be tried. If a message did not match any of the regular
expressions then it is discarded and an error code is returned to the client. An
example of a Plexer configuration is shown below.
%% What is the order testing the regular expressions. First listed first tested or Last listed firsted tested?

\begin{lstlisting}[language=xml]
...
<Plexer>
  <next>^/arex$</next>
  <next>^/[eE][cC][hH][oO]$</next>
</Plexer>
...
\end{lstlisting}
